---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# democombine

<!-- badges: start -->
<!-- badges: end -->

The goal of democombine is to demonstrate an issue with using `dplyr::combine()` when you have your own `combine` function method.

## Installation

You can install the development version of democombine from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("njtierney/democombine")
```

## Example of issue

```{r}
library(democombine)

x <- my_class(1:10)
y <- my_class(20:10)

x
y

combine(x, y)
```

So that works fine, but then if you load dplyr, you get a namespace conflict, which overwrites the S3 method:

```{r}
library(dplyr)

combine(x, y)
```

You can resolve this with `conflicted`. But I'm wondering if there's a way to force `dplyr::combine` to be turned into an S3 method so we can use our own `combine` method?

